Tempo Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 2

### 2022-08-30 experiment-2/analysis/teaching/teaching_art.Rmd
upload analysis between those who had teaching experience vs those who didn't
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Articulation Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

2. Excluded participants

- SubNr 1: A deviated tempo
- SubNr 3: Experimental error
- SubNr 8: Experimental error
- SubNr 14: Experimental error
- SubNr 16: A deviated tempo

@@

# read info about teaching experience
source(here("experiment-1/analysis/demographics", "questionnaire.R"), chdir = TRUE)
```

```{r file, include = FALSE}
filename_ioi = "../preprocessor/trimmed/data_analysis_ioi.txt"
filename_kot = "../preprocessor/trimmed/data_analysis_kot.txt"
```

```{r extract, include = FALSE}
dt_ioi <- fread(filename_ioi, header = T, sep = ",", dec = ".") # read a trimmed txt
dt_kot <- fread(filename_kot, header = T, sep = ",", dec = ".") # read a trimmed txt

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)
dt_kot$SubNr <- as.factor(dt_kot$SubNr)

# For each individual, each block, each trial
ioi <- dt_ioi[, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Condition, Skill)]

# Calculate KOR for each interval (outliers were already determined based on KOT)
dt_kor <- data.table()
for (subnr in unique(dt_kot$SubNr)){
  for (block in unique(dt_kot[SubNr == subnr]$BlockNr)){
    for (trial in unique(dt_kot[SubNr == subnr & BlockNr == block]$TrialNr)){
      dt_current <- dt_kot[SubNr == subnr & BlockNr == block & TrialNr == trial]
      dt_current$KOR <- dt_current$KOT/ioi[SubNr == subnr & ioi$BlockNr == block & TrialNr == trial]$Mean
      dt_kor <- rbind(dt_kor, dt_current)
    }
  }
}

# Include only articulation
dt_kot_art <- dt_kot[Skill == "articulation"]
dt_kor_art <- dt_kor[Skill == "articulation"]

# Include only dynamics
dt_kot_dyn <- dt_kot[Skill == "dynamics"]
dt_kor_dyn <- dt_kor[Skill == "dynamics"]
```

@@

# add teaching info
kot_art$Teaching <- rep(dt_included$TeachingPiano, each = 4)
kot_art$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
kot_art
```

@@

### Plot
#### Box plot
```{r kot-art-all-box, echo = FALSE}
kot_art_plot <- data.table(subject = kot_art[Condition == "teaching"]$SubNr, teaching = kot_art[Condition == "teaching"]$Mean, performing = kot_art[Condition == "performing"]$Mean, subcomponent = kot_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

@@

# add teaching info
kor_art$Teaching <- rep(dt_included$TeachingPiano, each = 4)
kor_art$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
kor_art
```

@@

### Plot
#### Box plot
```{r kor-art-all-box, echo = FALSE}
kor_art_plot <- data.table(subject = kor_art[Condition == "teaching"]$SubNr, teaching = kor_art[Condition == "teaching"]$Mean, performing = kor_art[Condition == "performing"]$Mean, subcomponent = kor_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

@@

# add teaching info
kot_dyn$Teaching <- rep(dt_included$TeachingPiano, each = 4)
kot_dyn$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
kot_dyn
```

@@

### Plot
#### Box plot
```{r kot-dyn-all-box, echo = FALSE}
kot_dyn_plot <- data.table(subject = kot_dyn[Condition == "teaching"]$SubNr, teaching = kot_dyn[Condition == "teaching"]$Mean, performing = kot_dyn[Condition == "performing"]$Mean, subcomponent = kot_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

@@

# add teaching info
kor_dyn$Teaching <- rep(dt_included$TeachingPiano, each = 4)
kor_dyn$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
kor_dyn
```

@@

### Plot
#### Box plot
```{r kor-dyn-all-box, echo = FALSE}
kor_dyn_plot <- data.table(subject = kor_dyn[Condition == "teaching"]$SubNr, teaching = kor_dyn[Condition == "teaching"]$Mean, performing = kor_dyn[Condition == "performing"]$Mean, subcomponent = kor_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

>>>>

---
title: 'Articulation Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 2'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

2. Excluded participants
- SubNr 3: Insufficient motor skills

@@

# read info about teaching experience
source(here("experiment-2/analysis/demographics", "questionnaire.R"), chdir = TRUE)
```

```{r file, include = FALSE}
filename_kor = "../preprocessor/trimmed/data_analysis_kor.txt"
filename_kot = "../preprocessor/trimmed/data_analysis_kot.txt"
```

```{r extract, include = FALSE}
dt_kor <- fread(filename_kor, header = T, sep = ",", dec = ".") # read a trimmed txt
dt_kot <- fread(filename_kot, header = T, sep = ",", dec = ".") # read a trimmed txt

# SubNr as a factor
dt_kor$SubNr <- as.factor(dt_kor$SubNr)
dt_kot$SubNr <- as.factor(dt_kot$SubNr)

# Include only articulation
dt_kor_art <- dt_kor[Skill == "articulation"]
dt_kot_art <- dt_kot[Skill == "articulation"]

# Include only dynamics
dt_kor_dyn <- dt_kor[Skill == "dynamics"]
dt_kot_dyn <- dt_kot[Skill == "dynamics"]
```

@@

# add teaching info
kot_art$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
kot_art$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
kot_art
```

@@

### Plot
#### Box plot
```{r kot-art-all-box, echo = FALSE}
kot_art_plot <- data.table(subject = kot_art[Condition == "teaching"]$SubNr, teaching = kot_art[Condition == "teaching"]$Mean, performing = kot_art[Condition == "performing"]$Mean, subcomponent = kot_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

@@

# add teaching info
kor_art$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
kor_art$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)

kor_art
```

@@

### Plot
#### Box plot
```{r kor-art-all-box, echo = FALSE}
kor_art_plot <- data.table(subject = kor_art[Condition == "teaching"]$SubNr, teaching = kor_art[Condition == "teaching"]$Mean, performing = kor_art[Condition == "performing"]$Mean, subcomponent = kor_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

@@

# add teaching info
kot_dyn$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
kot_dyn$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
kot_dyn
```

@@

### Plot
#### Box plot
```{r kot-dyn-all-box, echo = FALSE}
kot_dyn_plot <- data.table(subject = kot_dyn[Condition == "teaching"]$SubNr, teaching = kot_dyn[Condition == "teaching"]$Mean, performing = kot_dyn[Condition == "performing"]$Mean, subcomponent = kot_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

@@

# add teaching info
kor_dyn$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
kor_dyn$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
kor_dyn
```

@@

### Plot
#### Box plot
```{r kor-dyn-all-box, echo = FALSE}
kor_dyn_plot <- data.table(subject = kor_dyn[Condition == "teaching"]$SubNr, teaching = kor_dyn[Condition == "teaching"]$Mean, performing = kor_dyn[Condition == "performing"]$Mean, subcomponent = kor_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

### 2022-08-30 experiment-2/analysis/teaching/teaching_dyn.Rmd
upload analysis between those who had teaching experience vs those who didn't
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Dynamics Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# read info about teaching experience
source(here("experiment-1/analysis/demographics", "questionnaire.R"), chdir = TRUE)
```

@@

# add teaching info
vel_dyn$Teaching <- rep(dt_included$TeachingPiano, each = 4)
vel_dyn$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
vel_dyn
```

@@

### Plot
#### Box plot
```{r vel-dyn-all-box, echo = FALSE}
vel_dyn_plot <- data.table(subject = vel_dyn[Condition == "teaching"]$SubNr, teaching = vel_dyn[Condition == "teaching"]$Mean, performing = vel_dyn[Condition == "performing"]$Mean, subcomponent = vel_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

@@

```{r vel-diff-dyn, echo = FALSE}
# For each individual
vel_diff_dyn_trial <- dt_vel_diff_dyn[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Subcomponent)]

vel_diff_dyn <- vel_diff_dyn_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Condition, Skill, Subcomponent)]
setorder(vel_diff_dyn_trial, "SubNr", "Condition", "Skill", "Subcomponent")

@@

# add teaching info
vel_diff_dyn$Teaching <- rep(dt_included$TeachingPiano, each = 4)
vel_diff_dyn$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
vel_diff_dyn
```

@@

### Plot
#### Box plot
```{r vel-diff-dyn-all-box, echo = FALSE}
vel_diff_dyn_plot <- data.table(subject = vel_diff_dyn[Condition == "teaching"]$SubNr, teaching = vel_diff_dyn[Condition == "teaching"]$Mean, performing = vel_diff_dyn[Condition == "performing"]$Mean, subcomponent = vel_diff_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

@@

```{r vel-art, echo = FALSE}
# For each individual
vel_art_trial <- dt_vel_art[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Subcomponent)]

vel_art <- vel_art_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Condition, Skill, Subcomponent)]
setorder(vel_art, "SubNr", "Condition", "Skill", "Subcomponent")

# add teaching info
vel_art$Teaching <- rep(dt_included$TeachingPiano, each = 4)
vel_art$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)

vel_art
```

@@

### Plot
#### Box plot
```{r vel-art-all-box, echo = FALSE}
vel_art_plot <- data.table(subject = vel_art[Condition == "teaching"]$SubNr, teaching = vel_art[Condition == "teaching"]$Mean, performing = vel_art[Condition == "performing"]$Mean, subcomponent = vel_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

@@

# add teaching info
vel_diff_art$Teaching <- rep(dt_included$TeachingPiano, each = 4)
vel_diff_art$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 4)
vel_diff_art
```

@@

### Plot
#### Box plot
```{r vel-diff-art-all-box, echo = FALSE}
vel_diff_art_plot <- data.table(subject = vel_diff_art[Condition == "teaching"]$SubNr, teaching = vel_diff_art[Condition == "teaching"]$Mean, performing = vel_diff_art[Condition == "performing"]$Mean, subcomponent = vel_diff_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_included$TeachingPiano, each = 2), teachingyears = rep(dt_included$TeachingPianoYears, each = 2))

>>>>

---
title: 'Dynamics Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 2'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# read info about teaching experience
source(here("experiment-2/analysis/demographics", "questionnaire.R"), chdir = TRUE)
```

@@

# add teaching info
vel_dyn$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
vel_dyn$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
vel_dyn
```

@@

### Plot
#### Box plot
```{r vel-dyn-all-box, echo = FALSE}
vel_dyn_plot <- data.table(subject = vel_dyn[Condition == "teaching"]$SubNr, teaching = vel_dyn[Condition == "teaching"]$Mean, performing = vel_dyn[Condition == "performing"]$Mean, subcomponent = vel_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

@@

```{r vel-diff-dyn, echo = FALSE}
# For each individual
vel_diff_dyn_trial <- dt_vel_diff_dyn[Subcomponent == "FtoP" | Subcomponent == "PtoF", .(N = .N, Mean = mean(Diff), SD = sd(Diff)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Subcomponent)]
setorder(vel_diff_dyn_trial, "SubNr", "Condition", "Skill", "Subcomponent")

@@

# add teaching info
vel_diff_dyn$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
vel_diff_dyn$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
vel_diff_dyn
```

@@

### Plot
#### Box plot
```{r vel-diff-dyn-all-box, echo = FALSE}
vel_diff_dyn_plot <- data.table(subject = vel_diff_dyn[Condition == "teaching"]$SubNr, teaching = vel_diff_dyn[Condition == "teaching"]$Mean, performing = vel_diff_dyn[Condition == "performing"]$Mean, subcomponent = vel_diff_dyn[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

@@

```{r vel-art, echo = FALSE}
# For each individual
vel_art_trial <- dt_vel_art[, .(N = .N, Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, Condition, Skill, BlockNr, TrialNr, Subcomponent)]
setorder(vel_art_trial, "SubNr", "Condition", "Skill", "Subcomponent")

vel_art <- vel_art_trial[, .(N = .N, Mean = mean(Mean), SD = sd(Mean)), by = .(SubNr, Condition, Skill, Subcomponent)]

# add teaching info
vel_art$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
vel_art$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
vel_art
```

@@

### Plot
#### Box plot
```{r vel-art-all-box, echo = FALSE}
vel_art_plot <- data.table(subject = vel_art[Condition == "teaching"]$SubNr, teaching = vel_art[Condition == "teaching"]$Mean, performing = vel_art[Condition == "performing"]$Mean, subcomponent = vel_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

@@

# add teaching info
vel_diff_art$Teaching <- rep(dt_2_included$TeachingPiano, each = 4)
vel_diff_art$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 4)
vel_diff_art
```

@@

### Plot
#### Box plot
```{r vel-diff-art-all-box, echo = FALSE}
vel_diff_art_plot <- data.table(subject = vel_diff_art[Condition == "teaching"]$SubNr, teaching = vel_diff_art[Condition == "teaching"]$Mean, performing = vel_diff_art[Condition == "performing"]$Mean, subcomponent = vel_diff_art[Condition == "teaching"]$Subcomponent, teachingexp = rep(dt_2_included$TeachingPiano, each = 2), teachingyears = rep(dt_2_included$TeachingPianoYears, each = 2))

### 2022-08-30 experiment-2/analysis/teaching/teaching_ioi.Rmd
upload analysis between those who had teaching experience vs those who didn't
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Tempo Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 1'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# add teaching info
ioi_art$Teaching <- rep(dt_included$TeachingPiano, each = 2)
ioi_art$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 2)
ioi_art
```

@@

```{r ioi-art-all-box, echo = FALSE}
ioi_art_plot <- data.table(subject = ioi_art[Condition == "teaching"]$SubNr, teaching = ioi_art[Condition == "teaching"]$Mean, performing = ioi_art[Condition == "performing"]$Mean, teachingexp = dt_included$TeachingPiano, teachingyears = dt_included$TeachingPianoYears)

ggpaired(ioi_art_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "teachingexp", line.size = 0.3, line.color = "gray", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation") + geom_hline(yintercept = 188, linetype = "dashed")
```

@@

# add teaching info
ioi_dyn$Teaching <- rep(dt_included$TeachingPiano, each = 2)
ioi_dyn$TeachingYears <- rep(dt_included$TeachingPianoYears, each = 2)
ioi_dyn
```

@@

```{r ioi-dyn-all-box, echo = FALSE}
ioi_dyn_plot <- data.table(subject = ioi_dyn[Condition == "teaching"]$SubNr, teaching = ioi_dyn[Condition == "teaching"]$Mean, performing = ioi_dyn[Condition == "performing"]$Mean, teachingexp = dt_included$TeachingPiano, teachingyears = dt_included$TeachingPianoYears)

ggpaired(ioi_dyn_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "teachingexp", line.size = 0.3, line.color = "gray", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Dynamics") + geom_hline(yintercept = 188, linetype = "dashed")
```

>>>>

---
title: 'Tempo Analysis (Teaching vs. Non-Teaching): The Sound of Teaching Music 2'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# add teaching info
ioi_art$Teaching <- rep(dt_2_included$TeachingPiano, each = 2)
ioi_art$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 2)
ioi_art
```

@@

```{r ioi-art-all-box, echo = FALSE}
ioi_art_plot <- data.table(subject = ioi_art[Condition == "teaching"]$SubNr, teaching = ioi_art[Condition == "teaching"]$Mean, performing = ioi_art[Condition == "performing"]$Mean, teachingexp = dt_2_included$TeachingPiano, teachingyears = dt_2_included$TeachingPianoYears)

ggpaired(ioi_art_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "teachingexp", line.size = 0.3, line.color = "gray", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Articulation")
```

@@

# add teaching info
ioi_dyn$Teaching <- rep(dt_2_included$TeachingPiano, each = 2)
ioi_dyn$TeachingYears <- rep(dt_2_included$TeachingPianoYears, each = 2)
ioi_dyn
```

@@

```{r ioi-dyn-all-box, echo = FALSE}
ioi_dyn_plot <- data.table(subject = ioi_dyn[Condition == "teaching"]$SubNr, teaching = ioi_dyn[Condition == "teaching"]$Mean, performing = ioi_dyn[Condition == "performing"]$Mean, teachingexp = dt_2_included$TeachingPiano, teachingyears = dt_2_included$TeachingPianoYears)

ggpaired(ioi_dyn_plot, cond1 = "performing", cond2 = "teaching", color = "condition", facet.by = "teachingexp", line.size = 0.3, line.color = "gray", xlab = "Condition", ylab = "IOIs (ms)", title = "IOI: Dynamics")
```
